Basic polisci-style AMCEs and MMs

### 2023-09-08 notebook/basic-amces-mms.qmd
Reorganize and standardize notebook

```{r libraries-data, warning=FALSE, message=FALSE}
library(tidyverse)
library(cregg)

results_long <- readRDS("original_data.rds") %>% 
  mutate(choice_binary = ifelse(choice == alt, 1, 0)) %>%
  mutate(choice_alt = factor(alt * choice_binary)) %>% 
  mutate(
    feat_transp = fct_relabel(feat_transp, ~paste("Transparency: ", .x)),
    feat_acc = fct_relabel(feat_acc, ~paste("Accountability: ", .x)),
  )
```

>>>>

```{r libraries-data, warning=FALSE, message=FALSE}
library(tidyverse)
library(cregg)
library(targets)

# Targets stuff
tar_config_set(store = here::here('_targets'),
               script = here::here('_targets.R'))

results_long <- tar_read(data_full) %>% 
  mutate(
    feat_transp = fct_relabel(feat_transp, ~paste("Transparency: ", .x)),
    feat_acc = fct_relabel(feat_acc, ~paste("Accountability: ", .x)),
  )
```
